---
title: "Let's shine the dashboard!"
author: "Novo Nordisk A/S"
date: "`r Sys.Date()`"
output: html_document
---

# Introduction

### First steps

*R Markdown* is a file format for making dynamic documents with R. An _RMarkdown_ document is written in markdown (an easy-to-write plain text format) and contains chunks of embedded R code

R Markdown reports rely on three frameworks

1. _markdown_ for formatted text
2. _knitr_ for embedded R code
3. _YAML_ for render parameters

#### Markdown

Markdown is an **easy to use** format for writing reports. It resembles what you naturally write every time you compose an email. In fact, you may have already used markdown *without realizing it*. These websites all rely on markdown formatting

* [Github](www.github.com)
* [StackOverflow](www.stackoverflow.com)
* [Reddit](www.reddit.com)

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, message=FALSE, include=FALSE}
library(haven)
library(dplyr)
library(ggplot2)
```

```{r, include=FALSE}

adae <- read_xpt(url("https://github.com/cdisc-org/sdtm-adam-pilot-project/blob/master/updated-pilot-submission-package/900172/m5/datasets/cdiscpilot01/analysis/adam/datasets/adae.xpt?raw=true"))
adsl <- read_xpt(url("https://github.com/cdisc-org/sdtm-adam-pilot-project/blob/master/updated-pilot-submission-package/900172/m5/datasets/cdiscpilot01/analysis/adam/datasets/adsl.xpt?raw=true"))
advs <- read_xpt(url("https://github.com/cdisc-org/sdtm-adam-pilot-project/blob/master/updated-pilot-submission-package/900172/m5/datasets/cdiscpilot01/analysis/adam/datasets/advs.xpt?raw=true"))
```


# Adding plots

### Bar plot

```{r pressure, echo=FALSE, fig.cap="Barplot for age group", fig.dim=.25}
adsl %>%
  filter(SAFFL == "Y") %>%
  ggplot(aes(x = AGEGR1, fill = TRT01A)) +
    geom_bar()
```


### Box plot
```{r, fig.width=10, fig.height=5}
adsl %>%
  filter(SAFFL == "Y") %>%
  ggplot(aes(x = SEX, y = AGE, fill = TRT01A)) +
    geom_boxplot() +
    xlab("Sex") +
    ylab("Age")
```

# Adding tables

### All subjects more than 85 years old


```{r echo=FALSE}
adsl_over85 <- adsl %>%
  filter(AGE > 85) %>%
  select(USUBJID, AGE, WEIGHTBL, BMIBL, TRT01P, SEX)

knitr::kable(adsl_over85)

# html only
# DT::datatable(adsl_over85)

```



### Inline code
The number of subject in SAF is `r adsl %>% filter(SAFFL == 'Y') %>% count()`.


# Mathematics

## Equations

$\overline{x}=\frac{\sum_{i=1}^n}{n}$

$\overline{x}=\frac{x_{1} + x_{2} + \cdots + x_{n}}{n}$
